Low prevalence of \emph{a priori} power analyses in motor behavior research

### 2022-10-19 docs/revision-1/r1_manuscript.Rmd
update: italicize journal names

\textcolor{blue}{Studies published in Human Movement Science included a power analysis (59/271) 18\% of the time, the Journal of Motor Learning and Development (9/128) 10\% of the time, and the Journal of Motor Behavior (16/152) 7\% of the time. The 3-samples proportions test was significant, $\chi^2$ = 13.52, \emph{df} = 2, \emph{p} = .001.}

@@

All three journals that we sampled from either explicitly mention power in their instructions for authors (*Human Movement Science*), or reference JARS (*Journal of Motor Learning and Development*) or CONSORT (*Journal of Motor Behavior*) reporting standards; both of which include power analyses. \textcolor{blue}{Perhaps the approach of more directly instructing authors to include a power analysis explains why Human Movement Science had a higher proportion of studies with a power analysis. This post-hoc explanation is consistent with the modest increase in power analysis reporting observed following adoption of guidelines requiring sample size justification in the journal Gait \& Posture} [@McCrum2022]. \textcolor{blue}{ However, less than one in five studies in \emph{Human Movement Science} included a power analysis so including explicit instructions to authors is not sufficient to promote widespread reporting. It seems the} adoption of power analyses targeting interesting effects does not require a policy shift, simply the enforcement of current guidelines. Since no studies in this sample powered for the smallest effect size of interest, if *Human Movement Science*, the *Journal of Motor Behavior*, and/or the *Journal of Motor Learning and Development* enforce their existing guidelines then their future publications \textcolor{blue}{might} look dramatically different. \textcolor{blue}{Even if power analysis reporting becomes the norm, it may remain unclear whether power analyses were conducted during the design of the study or at a later stage. Therefore, the most credible confirmatory studies will have preregistered power analyses. A bold journal might even require it.} We believe this is a promising path forward to increase the reliability of motor behavior research and the evidence-based recommendations for coaching and rehabilitation.

>>>>

\textcolor{blue}{Studies published in \emph{Human Movement Science} included a power analysis (59/271) 18\% of the time, the \emph{Journal of Motor Learning and Development} (9/128) 10\% of the time, and the \emph{Journal of Motor Behavior} (16/152) 7\% of the time. The 3-samples proportions test was significant, $\chi^2$ = 13.52, \emph{df} = 2, \emph{p} = .001.}

@@

All three journals that we sampled from either explicitly mention power in their instructions for authors (*Human Movement Science*), or reference JARS (*Journal of Motor Learning and Development*) or CONSORT (*Journal of Motor Behavior*) reporting standards; both of which include power analyses. \textcolor{blue}{Perhaps the approach of more directly instructing authors to include a power analysis explains why \emph{Human Movement Science} had a higher proportion of studies with a power analysis. This post-hoc explanation is consistent with the modest increase in power analysis reporting observed following adoption of guidelines requiring sample size justification in the journal \emph{Gait \& Posture}} [@McCrum2022]. \textcolor{blue}{ However, less than one in five studies in \emph{Human Movement Science} included a power analysis so including explicit instructions to authors is not sufficient to promote widespread reporting. It seems the} adoption of power analyses targeting interesting effects does not require a policy shift, simply the enforcement of current guidelines. Since no studies in this sample powered for the smallest effect size of interest, if *Human Movement Science*, the *Journal of Motor Behavior*, and/or the *Journal of Motor Learning and Development* enforce their existing guidelines then their future publications \textcolor{blue}{might} look dramatically different. \textcolor{blue}{Even if power analysis reporting becomes the norm, it may remain unclear whether power analyses were conducted during the design of the study or at a later stage. Therefore, the most credible confirmatory studies will have preregistered power analyses. A bold journal might even require it.} We believe this is a promising path forward to increase the reliability of motor behavior research and the evidence-based recommendations for coaching and rehabilitation.

### 2022-10-19 docs/revision-1/r1_manuscript.tex
update: italicize journal names

All three journals that we sampled from either explicitly mention power in their instructions for authors (\emph{Human Movement Science}), or reference JARS (\emph{Journal of Motor Learning and Development}) or CONSORT (\emph{Journal of Motor Behavior}) reporting standards; both of which include power analyses. \textcolor{blue}{Perhaps the approach of more directly instructing authors to include a power analysis explains why Human Movement Science had a higher proportion of studies with a power analysis. This post-hoc explanation is consistent with the modest increase in power analysis reporting observed following adoption of guidelines requiring sample size justification in the journal Gait \& Posture} (McCrum et al., 2022). \textcolor{blue}{ However, less than one in five studies in \emph{Human Movement Science} included a power analysis so including explicit instructions to authors is not sufficient to promote widespread reporting. It seems the} adoption of power analyses targeting interesting effects does not require a policy shift, simply the enforcement of current guidelines. Since no studies in this sample powered for the smallest effect size of interest, if \emph{Human Movement Science}, the \emph{Journal of Motor Behavior}, and/or the \emph{Journal of Motor Learning and Development} enforce their existing guidelines then their future publications \textcolor{blue}{might} look dramatically different. \textcolor{blue}{Even if power analysis reporting becomes the norm, it may remain unclear whether power analyses were conducted during the design of the study or at a later stage. Therefore, the most credible confirmatory studies will have preregistered power analyses. A bold journal might even require it.} We believe this is a promising path forward to increase the reliability of motor behavior research and the evidence-based recommendations for coaching and rehabilitation.

>>>>

All three journals that we sampled from either explicitly mention power in their instructions for authors (\emph{Human Movement Science}), or reference JARS (\emph{Journal of Motor Learning and Development}) or CONSORT (\emph{Journal of Motor Behavior}) reporting standards; both of which include power analyses. \textcolor{blue}{Perhaps the approach of more directly instructing authors to include a power analysis explains why \emph{Human Movement Science} had a higher proportion of studies with a power analysis. This post-hoc explanation is consistent with the modest increase in power analysis reporting observed following adoption of guidelines requiring sample size justification in the journal \emph{Gait \& Posture}} (McCrum et al., 2022). \textcolor{blue}{ However, less than one in five studies in \emph{Human Movement Science} included a power analysis so including explicit instructions to authors is not sufficient to promote widespread reporting. It seems the} adoption of power analyses targeting interesting effects does not require a policy shift, simply the enforcement of current guidelines. Since no studies in this sample powered for the smallest effect size of interest, if \emph{Human Movement Science}, the \emph{Journal of Motor Behavior}, and/or the \emph{Journal of Motor Learning and Development} enforce their existing guidelines then their future publications \textcolor{blue}{might} look dramatically different. \textcolor{blue}{Even if power analysis reporting becomes the norm, it may remain unclear whether power analyses were conducted during the design of the study or at a later stage. Therefore, the most credible confirmatory studies will have preregistered power analyses. A bold journal might even require it.} We believe this is a promising path forward to increase the reliability of motor behavior research and the evidence-based recommendations for coaching and rehabilitation.
